quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-18 paper-quollr.Rmd
Updated Figure 2

sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.25, 1.25)

scurve_umap_plt <- ggplot(
  scurve_umap_scaled, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5) +
  interior_annotation("a") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

hex_grid_poly_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = h), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice) + 
  interior_annotation("b") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

hex_centroids_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = h), 
               fill = "#ffffff")  +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#FF7755") +
  interior_annotation("c") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

wireframe_scurve <- ggplot() +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#FF7755") +
  interior_annotation("d") +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

@@

scurve_umap_plt + hex_grid_poly_scurve +
  hex_centroids_scurve + wireframe_scurve + 
  scurve_proj_umap_model1 +
  plot_layout(ncol = 5)
```

>>>>

sc_xlims <- c(-0.25, 1.35)
sc_ylims <- c(-0.25, 1.35)

scurve_umap_plt <- ggplot(
  scurve_umap_scaled, 
  aes(x = emb1, y = emb2)) +
  geom_point(alpha = 0.5, color = clr_choice, size = 0.5) +
  interior_annotation("a", cex = 3) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

hex_grid_poly_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = h), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice) + 
  interior_annotation("b", cex = 3) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

hex_centroids_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = h), 
               fill = "#ffffff")  +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#FF7755") +
  interior_annotation("c", cex = 3) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

wireframe_scurve <- ggplot() +
  geom_segment(data = tr_from_to_df_scurve,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = df_bin_centroids_scurve, 
             aes(x = c_x, y = c_y), 
             size = 1, color = "#FF7755") +
  interior_annotation("d", cex = 3) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

scurve_proj_umap_model1_dp <- plot_proj(
  proj_obj = proj_obj1,
  point_param = c(0.2, 0, clr_choice), # size, alpha, color
  plot_limits = c(-0.35, 0.35), 
  axis_text_size = 7,
  is_category = FALSE) +
  interior_annotation(label = "e", cex = 3)

@@

scurve_umap_plt + hex_grid_poly_scurve +
  hex_centroids_scurve + wireframe_scurve + 
  scurve_proj_umap_model1_dp +
  plot_layout(ncol = 5)
```
